Supplementary Figures relative to clustering

### 2020-02-27 supplementary_figures/supp1_dataset_description.Rmd
updated supplementary figures

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(SingleCellExperiment)
  library(scater)
  library(reshape2)
  library(pheatmap)
  library(pipeComp)
})
source("../misc_functions.R")
theme_set(theme_cowplot(font_size = 12))
# we load the datasets
lf <- list.files("../datasets/", full.names=TRUE)
names(lf) <- gsub(".SCE.rds", "", basename(lf), fixed=TRUE)
lf <- lf[grep("simMix", lf, invert=TRUE)]
SCEs <- lapply(lf, readRDS)
```

```{r dist_cell_properties, fig.width=8.5, fig.height=8.5}
vars <- c( "log10(features)"="log10_total_features", "log10(counts)"="log10_total_counts", 
           "% in top 20"="pct_counts_in_top_20_features", "% mito"="pct_counts_Mt", 
           "% ribosomal"="pct_counts_ribosomal", "% coding"="pct_counts_coding" )
plot_grid(plotlist=lapply(1:length(vars), FUN=function(x){ 
  p <- plotFilters(SCEs, vars[x], nmads=c(2,5), ncol=1) + xlab(names(vars)[x])
  p <- p + scale_y_continuous(breaks=scales::pretty_breaks(2))
  p <- p + scale_x_continuous(breaks=scales::pretty_breaks(3))
  p + theme( axis.title.y = element_blank(), 
             strip.text.x = element_text(size=10),
             axis.title=element_text(size=11),
             axis.text=element_text(size=11) )
}), nrow=1)
```

@@

@@

>>>>

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(SingleCellExperiment)
  library(scater)
  library(reshape2)
  library(pheatmap)
  library(pipeComp)
})
source("../misc_functions.R")
# we load the datasets
lf <- list.files("../datasets/", full.names=TRUE)
names(lf) <- gsub(".SCE.rds", "", basename(lf), fixed=TRUE)
lf <- lf[grep("simMix", lf, invert=TRUE)]
SCEs <- lapply(lf, readRDS)
```

@@

```{r dist_cell_properties, fig.width=8.5, fig.height=8.5}
theme_set(theme_cowplot(font_size = 12))
vars <- c( "log10(features)"="log10_total_features", "log10(counts)"="log10_total_counts", 
           "% in top 20"="pct_counts_in_top_20_features", "% mito"="pct_counts_Mt", 
           "% ribosomal"="pct_counts_ribosomal", "% coding"="pct_counts_coding" )
plot_grid(plotlist=lapply(1:length(vars), FUN=function(x){ 
  p <- plotFilters(SCEs, vars[x], nmads=c(2,5), ncol=1) + xlab(names(vars)[x])
  p <- p + scale_y_continuous(breaks=scales::pretty_breaks(2))
  p <- p + scale_x_continuous(breaks=scales::pretty_breaks(3))
  p + theme( axis.title.y = element_blank(), 
             strip.text.x = element_text(size=10),
             axis.title=element_text(size=11),
             axis.text=element_text(size=11) )
}), nrow=1)
```

@@

### Supplementary Figure `r getFigNb()`
Relationship between selected cell-level QC metrics.

### 2020-02-27 supplementary_figures/supp2_filtering.Rmd
updated supplementary figures

```{r filt_more, fig.width=8, fig.height=9}
res <- readRDS("../data/results_filtering.rds")
m <- scrna_evalPlot_filtering(res, returnTable=TRUE)
m <- m[grep("veryStringent", m$method, invert=TRUE),]

>>>>

```{r filt_more, fig.width=8, fig.height=9}
res <- readRDS("../data/results_filtering.rds")
m <- old_evalPlot_filtering(res, returnTable=TRUE)
m <- m[grep("veryStringent", m$method, invert=TRUE),]

### 2020-02-27 supplementary_figures/supp3_normalization.Rmd
updated supplementary figures

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(reshape2)
  library(dplyr)
  library(viridis)
  library(pipeComp)
})
suppressMessages(devtools::load_all("../../pipComp/"))
theme_set(theme_cowplot(font_size = 11))
source("../misc_functions.R")
```

@@

>>>>

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(reshape2)
  library(dplyr)
  library(viridis)
  library(pipeComp)
})
theme_set(theme_cowplot(font_size = 11))
source("../misc_functions.R")
```

@@

\newpage

```{r VST, echo=FALSE, out.width = '100%'}
knitr::include_graphics("vst.png")
```

### Supplementary Figure `r getFigNb()`
Relationship of the variance with mean count after `sctranform`'s variance stabilizing transformation.

\newpage

### 2020-02-27 supplementary_figures/supp4_selection.Rmd
updated supplementary figures

ds <- sapply(strsplit(colnames(cl)," "), FUN=function(x) x[1])
ds <- split(seq_len(ncol(cl)), ds)
ds <- ds[grep("stepElapsed",names(ds),invert=TRUE)]
myag <- function(cl, out="ARI", trueK=FALSE){
  y <- lapply(ds, FUN=function(x){
    x <- cl[,x]
    colnames(x) <- sapply(strsplit(colnames(x)," "), FUN=function(x) x[2])
    x <- parsePipNames(x)
    if(!trueK) return( aggregate( x[,out], 
                                  by=list(method=x$sel, nb=x$selnb), 
                                  na.rm=TRUE, FUN=mean) )
    w <- which(x$n_clus==x$true.nbClusts)
    aggregate(x[w,out], by=list(method=x$sel[w], nb=x$selnb[w]), na.rm=TRUE, FUN=mean)
  })
  bind_rows(y, .id="dataset")
}
vst.ARIatK <- myag(vst, trueK=TRUE)
snorm.ARIatK <- myag(snorm, trueK=TRUE)

>>>>

ds <- sapply(strsplit(colnames(cl)," "), FUN=function(x) x[1])
ds <- split(seq_len(ncol(cl)), ds)
ds <- ds[grep("stepElapsed",names(ds),invert=TRUE)]
myag <- function(cl, out="ARI", trueK=FALSE){
  y <- lapply(ds, FUN=function(x){
    x <- cl[,x]
    colnames(x) <- sapply(strsplit(colnames(x)," "), FUN=function(x) x[2])
    x <- parsePipNames(x)
    if(!trueK) return( aggregate( x[,out], 
                                  by=list(method=x$sel, nb=x$selnb), 
                                  na.rm=TRUE, FUN=mean) )
    w <- which(x$n_clus==x$true.nbClusts)
    aggregate(x[w,out], by=list(method=x$sel[w], nb=x$selnb[w]), na.rm=TRUE, FUN=mean)
  })
  dplyr::bind_rows(y, .id="dataset")
}
vst.ARIatK <- myag(vst, trueK=TRUE)
snorm.ARIatK <- myag(snorm, trueK=TRUE)

### 2020-02-27 supplementary_figures/supp6_clust.Rmd
updated supplementary figures

suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(reshape2)
  library(dplyr)
  library(patchwork)
})
theme_set(theme_cowplot(font_size = 12))
devtools::load_all("../../pipeComp/")
source("../misc_functions.R")
```

@@

```{r, include=FALSE}
#res <- readRDS("../data/clust_endSummary.rds")
res <- readRDS("../data/results_clust_2.rds")
res <- parsePipNames(res$clustering)
res <- res[which(res$norm=="norm.seurat" & res$resolution <5),]
x <- grep("true\\.nbClusts",colnames(res),value=TRUE)
names(x) <- x <- sapply(strsplit(x," "),FUN=function(x) x[[1]])
y <- cbind(res[,c("k","steps","resolution","clustmethod","dims")],sapply(x, FUN=function(x){
  res[[paste(x,"n_clus")]] - res[[paste(x,"true.nbClusts")]]
}))
y$param <- ifelse( res$clustmethod=="clust.seurat", paste0(" res=",res$resolution), paste0(" steps=",res$steps))
ag <- aggregate(y[,names(x)], by=y[,c("clustmethod", "k","param"),drop=FALSE], FUN=mean)
agl <- cbind(ag[rep(1:nrow(ag), 9),1:3], dataset=rep(colnames(ag)[4:ncol(ag)], each=nrow(ag)), delta=as.numeric(as.matrix(ag[,4:ncol(ag)])))
agl$k <- factor(agl$k, as.character(sort(unique(agl$k))))
x <- sapply(unique(strsplit(ag$param, "=")), FUN=function(x) as.numeric(x[[2]]) )
names(x) <- unique(ag$param)
agl$param <- factor(agl$param, names(sort(x)))

@@

```{r, fig.width=8, fig.height=8}
(pf(agl[which(agl$clustmethod=="clust.seurat"),]) + ylab("Seurat") + theme(legend.position = "top")) / 
    (pf(agl[which(agl$clustmethod=="clust.scran"),]) + ylab("scran walktrap")) /
    (pf(agl[which(agl$clustmethod=="clust.scran.fg"),]) + ylab("scran fast_greedy")) /
    (ggplot(agl, aes(k)) + theme(axis.line.y=element_blank(), plot.margin = unit(rep(0,4),"pt"))) + 
    plot_layout(heights = c(10,8,8,1))
```

>>>>

suppressPackageStartupMessages({
  library(ggplot2)
  library(cowplot)
  library(ComplexHeatmap)
  library(reshape2)
  library(dplyr)
  library(patchwork)
  library(pipeComp) # (requires `pipeComp` version >=0.99.3)
  library(scales)
})
theme_set(theme_cowplot(font_size = 12))
source("../misc_functions.R")
```

@@

```{r, include=FALSE}
res <- readRDS("../data/results_clustering2.rds")
res <- res$evaluation$clustering
res <- res[which(res$norm=="norm.seurat" & res$resolution <5),]
res$delta <- res$n_clus-res$true.nbClusts
res$param <- ifelse( res$clustmethod=="clust.seurat", paste0(" res=",res$resolution), paste0(" steps=",res$steps))
res$param[which(res$clustmethod=="clust.scran.fg")] <- "NA"
agl <- aggregate(res[,"delta",drop=FALSE], by=res[,c("dataset","clustmethod", "k","param"),drop=FALSE], FUN=mean)
agl$k <- factor(agl$k, as.character(sort(unique(agl$k))))
x <- sapply(unique(strsplit(agl$param, "=")), FUN=function(x){
  tryCatch(as.numeric(x[[2]]), error=function(e) NA_real_)
})
names(x) <- unique(agl$param)
agl$param <- factor(agl$param, names(sort(x)))

@@

```{r, fig.width=8, fig.height=8}
tt <- theme(strip.background = element_blank(), strip.text.x = element_blank())
p1 <- pf(agl[which(agl$clustmethod=="clust.seurat"),]) + ylab("Seurat") + 
  theme(legend.position = "top", strip.text.x = element_text(size = 10, angle=60), strip.background = element_blank())
p1 / 
    (pf(agl[which(agl$clustmethod=="clust.scran"),]) + ylab("scran walktrap") + tt) /
    (pf(agl[which(agl$clustmethod=="clust.scran.fg"),]) + ylab("scran fast_greedy") + tt) /
    (ggplot(agl, aes(k)) + theme(axis.line.y=element_blank(), plot.margin = unit(rep(0,4),"pt"))) + 
    plot_layout(heights = c(10,6,2,1))
```
